Deep Variation Transformation for Foreground Detection

### 2019-02-09 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.aux
	modified:   draft.blg
	modified:   draft.log
	modified:   draft.out
	modified:   draft.pdf
	modified:   draft.tex

the training patches, which are used as the input of the network, are captured.

@@

and each of these patches is for $\frac{T}{N}$ pixels.

@@

In addition, for each pixel included in the patch, a label of the foreground or background is needed for training.

@@

%第四步空间近邻随机采样。
It is generally accepted that a pixel is not independent but related to its neighborhood,
and similar neighboring pixels share similar variations.
%
Therefore,
the spatial information should benefit from learning the pattern of pixels' variation.
%
With this motivation,
several training patches extracted from neighboring pixels are combined to improve the efficiency of the proposed approach.
%
In the experiments, three training patches are combined as follows:
\begin{equation}
    S_{x,y}(m,n) = \mathcal{C}o(S_{x,y}(m,n), S_{x', y'}(m,n), S_{x'', y ''}(m, n)),
\end{equation}
where the $\mathcal{C}o$ represents the concatenation process on the third dimension.
And neighboring patches are at pixel position $(x',y')$ and $(x'',y'')$ respectively.
% Ii is generally accepted that neighboring background pixels share a similar temporal distribution.
% %In other words, there are some clues hidden in pixels' spatial neighbors. 
% In order to benefit from the spatial context, we concatenate the pixel patch with 2 neighboring pixel patches, 
% 
% which are randomly selected in the 8-connected neighborhood of each pixel position. 
% The input patch of our network is defined as:
% \begin{equation}
%     S_{x,y}(m,n) = \mathcal{C}o(S_{x,y}(m,n), S_{x', y'}(m,n), S_{x'', y ''}(m, n)),
% \end{equation}
% where the $\mathcal{C}o$ represents the concatenation process on the third dimension.
% And neighboring patches are at pixel position $(x',y')$ and $(x'',y'')$ respectively.
% 
%In the previous steps, original videos are broken down into pixel patches which contain abundant background information.

\subsection*{Network Architecture and Variation Transformation}
% 先描述动机
As we mentioned above,
the main purpose of our DPVTL algorithm is the transformation between the sequence of pixels' observations with possibility of pixels belonging to foreground or background.
% the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
% into another space where the observations are easier classified.
% 分析问题，提出解决的方案，要用数学化的形式
Therefore,
our network entails learning a mapping from the input observations of pixels $s \in \mathcal{S}$ 
to the probability $p \in \mathcal{P}$ of the corresponding pixel belonging to foreground or background.
%
An end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels, as shown in the \reffig{flow_chart}.
%
Mathematically, the training procedure is as follows:
\begin{equation}
    \begin{split}
        \mathcal{P}(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} ( \mathcal{S}(m,n)) \cdots  ) )  \\
          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(\mathcal{S}(m,n)),
    \end{split}
\end{equation}
where $\mathcal{P}(x,y)$ is the probability, $\mathcal{S}(m,n)$ is the input patch of the network and $f_{\theta_i}$ represents different layers of the network.
% where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$. The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$. 
% Another advantage of symmetric padding is that the order information still remains.

@@

% 描述网络结构
%The network used in this work is devised as an end-to-end architecture XXX
The architecture of our FCN for foreground detection is illustrated in \reffig{flow_chart}. 
The proposed FCN contains 6 convolutional layers without pooling, and the filter size of the first five layers is set to $3\times 3$, compared to the last convolutional layer which has a filter size of $1\times 1$. 
We use the Rectified Linear Unit (ReLU) as the activation function after first three convolutional layers，
and the Sigmoid Cross Entropy loss function is applied to measures the performance of our network after the last convolutional layer. 
We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without extra optimization mechanism.

@@

\subsection{Foreground Detection}
%As shown in the \reffig{flow_chart}, 
After the transformation from observations to the probability of belonging to foreground or background,
the foreground is detected from the final binary mask.
%
During the transformation,
the pixel patches are fed into the network and transformed into the probability patches,
which are compared with a threshold $T_r$ for classification and then used to reconstruct the foreground to obtain the final results.
%
The comparison with a threshold is mathematically shown as:
\begin{equation}
    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
\end{equation}
where the $\mathcal{M}(x,y)$ is the final binary mask.
%
The $S'(x,y)$ is the probability of patches output by the network,
the $\mathcal{C}^{-1}$ is the reversed procedure of the reshape procedure shown in the \refeq{eq_reshape} and $R$ is the parameter for the reversing procedure of reshape.
%
$T_f$ is the threshold given by a user and $g()$ is the thresholding function shown in \refeq{piecewise_fg}.
% Then the reverse procedure of \refeq{eq_reshape}
% 
% used to reconstruct the foreground image for the final results.
% %
% 
% 
% The network devised in proposed approach 
% 
% 
% Then, the prediction maps can be reconstructed from the prediction patches.
% %
% Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
% %
% The threshold function is given by
\begin{equation}
    \label{piecewise_fg}
    g(x,y) =
 \begin{cases}
  1,  \quad x < y       \\
  0,  \quad otherwise   \\
\end{cases},
\end{equation}
%
%where the $M$ denotes the final foreground map given by our DPVTL model.

@@

\section{Experiments}
\label{sec5}
In this section, we ran comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW\cite{CAMO}.
%
The CDnet is the largest dataset for foreground detection as far as we are aware, containing 11 categories with several complex challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on. 
The CAMO-UOW is a challenging benchmark for camouflaged foreground detection, containing 10 high resolution videos. 
For each video, one or two persons appear in the scene with the clothes having similar color as the background.

The proposed approach is compared with several existing traditional state-of-the-art foreground detection algorithms, including IUTIS-5\cite{Bianco2017TEC}, SuBSENSE\cite{St-Charles2015SuBSENSE}, WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method like PAWCS\cite{Charles2015PAWCS}, SemanticBGS\cite{Braham2017Semantic}, AAPSA\cite{RAMIREZALONSO2016990}, etc. 
Moreover, two deep learning based algorithms are also compared with the proposed approach, which including DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
The results of the compared algorithms are captured by the implementation provided by authors.
% \textcolor{red}{All the results of compared algorithms are provided by authors.}

During the comparison, the F-measure Space (Fm) has been used for evaluation. 
Fm is a general international standard in foreground detection which measures the segmentation accuracy by considering both recall and precision. 
The definition of Fm is as follows:
\begin{equation}
Fm= \frac{2\times precision \times recall}{precision + recall} = \frac{2TP}{2TP+FN+FP},
\end{equation}
% 
% 
% \begin{equation}
%     F=\frac{precision \dot recall}{precision - recall}  = \frac{2TP}{2TP+FN+FP},
% \end{equation}
%
where TP, FP, and FN are true positives, false positives, and false negatives respectively, computed in pixels of all test frames for each video.

@@

Quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
To keep the length of this paper reasonable, only several typical videos are selected for the qualitative comparisons and discussion. 
In the dynamic background scene, the video ``canoe'' is a typical challenging video which includes a large area of rippling water. 
The main challenge comes from the dynamic background, in which it is hard to describe the background by a single image. 
For this condition, since traditional foreground detection methods such as the SharedModel and the WeSamBE cannot describe the complex dynamical background, they fail to detect the people on the boat, as shown in the \reffig{results_chart}. 
Besides, the detected moving objects of the SharedModel are not accurate in the boundary due to the utilization of texture features. 
In contrast, benefiting from the strong learning ability of Deep Learning networks, DeepBS successfully detects the people. 
Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even this algorithm suffers from poor detection of the boat shape. 
In contrast, the proposed approach performs superior to others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence. 
Based on this insight, the FCN network focuses on learning the patterns of pixel variation rather than a static background image.
Thus proposed approach achieves promising performance for the canoe video.

As for the case of shadow scene, ``peopleInShade'' is a typical example with prevalent hard and soft shadows. 
For traditional approaches, these shadow regions are usually segmented as foreground since they also movie with the objects. 
Therefore, traditional methods like PAWCS, WeSamBE and SharedModel falsely segment part of shadows as moving objects. 
In addition, the foreground provided by IUTIS-5 is incomplete on part of the pedestrian's body due to the interference of shades, 
because of the severe dependency on texture features. 
Whereas, DeepBS performs well for this video benefiting from the utilization of CNN. 
However, the shape of pedestrians are slightly deformed as a result of the patch-wise processing in CNN. 
In contrast, since our DPVL focusses on learning the pattern of pixels' variation in the shadow regions, 
the proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.

In the video ``corridor'' among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. 
Moreover, moving objects in these videos are exceedingly fuzzy and unclean, which is the main challenge for this category. 
WeSamBE, SharedModel and PAWCS successfully detect the target objects, because of a stable background in this indoor video. 
However, they fail to remove the reflections since their modeling ability has already reached a limit under the extreme condition of the thermal map. 
DeepBS, by contrast, succeeds in eliminating most of the reflections. 
Meanwhile, moving objects are also clearly divided from the background thanks to the strong modeling ability of CNN. 
However, due to the dependency of the edge feature, a small object was missed in the detection result. 
Fortunately, the proposed approach utilizes the pattern of pixels' variation, which is theoretically effective even in observations without color information. 
Consequently, our DPVL performs much better than other algorithms, with the most parts of the shadow being removed and the segmentation results become more accurate.

% \begin{table}[tab1]
\begin{table*}[!t]				% TABLE
\centering
\caption{The performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014. For each video, 100 frames were taken for the training of our FCN.}
\label{tab1}
\begin{tabular}{lllllllllllll}
\hline
Videos      & baseline & dyna.bg & cam.jitter & int.obj.m & shadow & thermal & bad.weat & low f.rate & night vid. & PTZ    & turbul. & overall \\ \hline
DeepBS\cite{Babaee2017deep}      & 0.9580   & 0.8761  & 0.8990     & 0.6097    & 0.9304 & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & 0.8993  & 0.7458  \\
IUTIS-5\cite{Bianco2017TEC}     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
FTSG\cite{Wang2014FTSG}        & 0.9330   & 0.8792  & 0.7513     & 0.7891    & 0.8832 & 0.7768  & 0.8228   & 0.6259     & 0.5130     & 0.3241 & 0.7127  & 0.7283  \\
AAPSA\cite{RAMIREZALONSO2016990}       & 0.9183   & 0.6706  & 0.7207     & 0.5098    & 0.7953 & 0.7030  & 0.7742   & 0.4942     & 0.4161     & 0.3302 & 0.4643  & 0.6179  \\
CwisarDH\cite{Gregorio2014CwisarDH}    & 0.9145   & 0.8274  & 0.7886     & 0.5753    & 0.8581 & 0.7866  & 0.6837   & 0.6406     & 0.3735     & 0.3218 & 0.7227  & 0.6812  \\
PAWCS\cite{Charles2015PAWCS}       & 0.9397   & 0.8938  & 0.8137     & 0.7764    & 0.8934 & 0.8324  & 0.8059   & 0.6433     & 0.4171     & 0.4450 & 0.7667  & 0.7403  \\
SuBSENSE\cite{St-Charles2015SuBSENSE}    & 0.9503   & 0.8177  & 0.8152     & 0.6569    & 0.8986 & 0.8171  & 0.8594   & 0.6594     & 0.4918     & 0.3894 & 0.8423  & 0.7408  \\
SemanticBGS\cite{Braham2017Semantic} & 0.9604   & \textbf{0.9489}  & 0.8388     & 0.7878    & 0.9244 & 0.8219  & 0.8260   & 0.7888     & 0.5014     & 0.5673 & 0.6921  & 0.7892  \\
MBS\cite{Multimode_Background_Subtraction}         & 0.9287   & 0.7915  & 0.8367     & 0.7568    & 0.8262 & 0.8194  & 0.7980   & 0.6350     & 0.5158     & 0.5520 & 0.5858  & 0.7288  \\
WeSamBE\cite{2017_TCSVT_BG_7938679}     & 0.9413   & 0.7440  & 0.7976     & 0.7392    & 0.8999 & 0.7962  & 0.8608   & 0.6602     & 0.5929     & 0.3844 & 0.7737  & 0.7446  \\
ShareM\cite{2015_ICME_ShareModel}      & 0.9522   & 0.8222  & 0.8141     & 0.6727    & 0.8898 & 0.8319  & 0.8480   & 0.7286     & 0.5419     & 0.3860 & 0.7339  & 0.7474  \\
GMM\cite{Zivkovic2004}         & 0.8245   & 0.633   & 0.5969     & 0.5207    & 0.7370 & 0.6621  & 0.7380   & 0.5373     & 0.4097     & 0.1522 & 0.4663  & 0.5707  \\
RMoG\cite{Varadarajan2013}        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
DPVT        & \textbf{0.9811}   & 0.9329  & \textbf{0.9014}     & \textbf{0.9595}    & \textbf{0.9467} & \textbf{0.9479}  & \textbf{0.8780}   & 0.7818     & \textbf{0.7737}     & \textbf{0.5957} & \textbf{0.9034}  & \textbf{0.8789} \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[!t]
\centering
\caption{The performance comparison of the proposed approach and some classical methods and deep-based method DBMF. For each video, 64 frames were taken for the training of our FCN.}
\label{tab2}
\begin{tabular}{llllllll}
\hline
Methods  & highway & office & Pedestrians & PETS2006 & Fall   & sofa   & overall \\ \hline
GMM\cite{Stauffer1999}      & 0.5788  & 0.2338 & 0.5202      & 0.6011   & 0.8026 & 0.5225 & 0.5432  \\
CodeBook\cite{WU2010739} & 0.8356  & 0.5939 & 0.7293      & 0.7808   & 0.3921 & 0.8149 & 0.6911  \\
ViBe\cite{Barnich2011_2011_TIP}     & 0.7535  & 0.6676 & 0.8367      & 0.6668   & 0.6829 & 0.4298 & 0.6729  \\
PBAS\cite{Hofmann2012Background}     & 0.8071  & 0.6839 & 0.7902      & 0.7280   & 0.3420 & 0.5768 & 0.6547  \\
P2M\cite{Yang2016P2M}      & 0.9160  & 0.3849 & 0.9121      & 0.7322   & 0.5819 & 0.4352 & 0.6604  \\
DBMF\cite{Yang2018DBMF}     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
DPVT     & \textbf{0.9888}  & \textbf{0.9819} & \textbf{0.9728}      & \textbf{0.9808}   & \textbf{0.9394} & \textbf{0.9333} & \textbf{0.9662}  \\ \hline
\end{tabular}
\end{table*}

>>>>

the training patches, which are used as the input to the network, are captured.

@@

and each of these patches has $\frac{T}{N}$ pixels.

@@

In addition, for each pixel included in a patch, a label of the foreground or background is needed for training.

@@

%第四步空间近邻随机采样。
It is generally accepted that a pixel is not independent but related to its neighborhood,
and similar neighboring pixels share similar variations.
%
Therefore,
spatial information should benefit from learning the pattern of pixels' variation.
%
With this motivation,
several training patches extracted from neighboring pixels are combined to improve the efficiency of the proposed approach.
%
In the experiments, three training patches are combined as follows:
\begin{equation}
    S_{x,y}(m,n) = \mathcal{C}o(S_{x,y}(m,n), S_{x', y'}(m,n), S_{x'', y ''}(m, n)),
\end{equation}
where $\mathcal{C}o$ represents the concatenation process on the third dimension.
And neighboring patches are at pixel position $(x',y')$ and $(x'',y'')$ respectively.
% Ii is generally accepted that neighboring background pixels share a similar temporal distribution.
% %In other words, there are some clues hidden in pixels' spatial neighbors. 
% In order to benefit from the spatial context, we concatenate the pixel patch with 2 neighboring pixel patches, 
% 
% which are randomly selected in the 8-connected neighborhood of each pixel position. 
% The input patch of our network is defined as:
% \begin{equation}
%     S_{x,y}(m,n) = \mathcal{C}o(S_{x,y}(m,n), S_{x', y'}(m,n), S_{x'', y ''}(m, n)),
% \end{equation}
% where the $\mathcal{C}o$ represents the concatenation process on the third dimension.
% And neighboring patches are at pixel position $(x',y')$ and $(x'',y'')$ respectively.
% 
%In the previous steps, original videos are broken down into pixel patches which contain abundant background information.

\subsection*{Network Architecture and Variation Transformation}
% 先描述动机
As we mentioned above,
the main purpose of our DPVTL algorithm is the transformation between the sequence of pixels' observations with possibility of pixels belonging to foreground or background.
% the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
% into another space where the observations are easier classified.
% 分析问题，提出解决的方案，要用数学化的形式
Therefore,
our network entails learning a mapping from the input observations of pixels $s \in \mathcal{S}$ 
to the probability $p \in \mathcal{P}$ of the corresponding pixel belonging to foreground or background.
%
An end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels, as shown in \reffig{flow_chart}.
%
Mathematically, the training procedure is as follows:
\begin{equation}
    \begin{split}
        \mathcal{P}(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} ( \mathcal{S}(m,n)) \cdots  ) )  \\
          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(\mathcal{S}(m,n)),
    \end{split}
\end{equation}
where $\mathcal{P}(x,y)$ is the probability, $\mathcal{S}(m,n)$ is the input patch of the network and $f_{\theta_i}$ represents different layers of the network.
% where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$. The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$. 
% Another advantage of symmetric padding is that the order information still remains.

@@

% 描述网络结构
%The network used in this work is devised as an end-to-end architecture XXX
The architecture of our FCN for foreground detection is illustrated in \reffig{flow_chart}. 
The proposed FCN contains 6 convolutional layers without pooling, and the filter size of the first five layers is set to $3\times 3$, compared to the last convolutional layer which has a filter size of $1\times 1$. 
We use the Rectified Linear Unit (ReLU) as the activation function after first three convolutional layers，
and the Sigmoid Cross Entropy loss function is applied to measures the performance of our network after the last convolutional layer. 
We do not use any other adjustment in our network training and the experimental results prove that the proposed approach is feasible and very effective.
After the thresholding calculations, our experiments show that a randomly initialized FCNs, 
trained end-to-end on feature learning can achieve state-of-the-art performance without any extra optimization mechanism.

@@

\subsection{Foreground Detection}
%As shown in the \reffig{flow_chart}, 
After the transformation from observations to the probability of belonging to foreground or background,
the foreground is detected from the final binary mask.
%
During the transformation,
the pixel patches are fed into the network and transformed into the probability patches,
which are compared with a threshold $T_r$ for classification and then used to reconstruct the foreground to obtain the final results.
%
Comparison with a threshold can be mathematically shown as:
\begin{equation}
    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
\end{equation}
where the $\mathcal{M}(x,y)$ is the final binary mask.
%
$S'(x,y)$ is the probability of patches output by the network,
$\mathcal{C}^{-1}$ is the reverse of the reshape procedure shown in \refeq{eq_reshape} and $R$ is the parameter for the reversing reshape procedure.
%
$T_f$ is the threshold given by a user and $g()$ is the thresholding function shown in \refeq{piecewise_fg}.
% Then the reverse procedure of \refeq{eq_reshape}
% 
% used to reconstruct the foreground image for the final results.
% %
% 
% 
% The network devised in proposed approach 
% 
% 
% Then, the prediction maps can be reconstructed from the prediction patches.
% %
% Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
% %
% The threshold function is given by
\begin{equation}
    \label{piecewise_fg}
    g(x,y) =
 \begin{cases}
  1,  \quad x < y       \\
  0,  \quad otherwise   \\
\end{cases},
\end{equation}
%
%where the $M$ denotes the final foreground map given by our DPVTL model.

@@

\section{Experiments}
\label{sec5}
In this section, we describe comprehensive experiments to evaluate the performance of the proposed approach on the CDnet 2014 benchmark\cite{CDN2014} and CAMO-UOW\cite{CAMO}.
%
CDnet is the largest dataset for foreground detection as far as we are kown, containing 11 categories with several complex challenging scenes, such as Dynamic Background, Camera Jitter, Shadow, Night Videos, PTZ and so on. 
The CAMO-UOW is a challenging benchmark for camouflaged foreground detection, containing 10 high resolution videos. 
For each video, one or two persons appear in the scene with clothes having color similar to the background.

The proposed approach is compared with several existing traditional state-of-the-art foreground detection algorithms, including IUTIS-5\cite{Bianco2017TEC}, SuBSENSE\cite{St-Charles2015SuBSENSE}, WeSamBE\cite{Jiang2017WeSamBE}, sharable GMM the SharedModel\cite{Chen2015SharedModel}, word-dictionaries-based method like PAWCS\cite{Charles2015PAWCS}, SemanticBGS\cite{Braham2017Semantic} and AAPSA\cite{RAMIREZALONSO2016990}.
Moreover, two deep learning based algorithms are also compared with the proposed approach, including DeepBS\cite{Babaee2017deep}, and DBMF\cite{Yang2018DBMF}. 
The results of the compared algorithms are captured by the implementation provided by the authors.
% \textcolor{red}{All the results of compared algorithms are provided by authors.}

For comparison, the F-measure Space (Fm) is used for evaluation. 
Fm is a general international standard in foreground detection which measures the segmentation accuracy by considering both recall and precision. 
The definition of Fm is as follows:
\begin{equation}
Fm= \frac{2\times precision \times recall}{precision + recall} = \frac{2TP}{2TP+FN+FP},
\end{equation}
% 
% 
% \begin{equation}
%     F=\frac{precision \dot recall}{precision - recall}  = \frac{2TP}{2TP+FN+FP},
% \end{equation}
%
where TP, FP, and FN are true positives, false positives, and false negatives respectively, computed on the pixels of all the test frames for each video.

@@

Quantitative and qualitative comparisons are shown in \reftab{tab1} and  \reffig{results_chart} respectively. 
To keep the length of this paper reasonable, only several typical videos are selected for the qualitative comparisons and discussion. 
In the dynamic background scene, the video ``canoe'' is a typical challenging video which includes a large area of rippling water. 
The main challenge comes from the dynamic background, in which it is hard to describe the background by a single image. 
For this condition, since traditional foreground detection methods such as the SharedModel and the WeSamBE cannot describe the complex dynamical background, they fail to detect the people on the boat, as shown in \reffig{results_chart}. 
Besides, the detected moving objects of the SharedModel are not accurate in the boundary due to the utilization of texture features. 
In contrast, benefiting from the strong learning ability of Deep Learning networks, DeepBS successfully detects the people. 
Unfortunately, since the DeepBS ignores the fact that a single background is not enough to describe the dynamic background, even this algorithm suffers from poor detection of the boat shape. 
In contrast, the proposed approach performs better from others in this scene, since the essence of foreground detection is considered as a binary classification of pixels' observation over a time sequence. 
Based on this insight, the FCN network focuses on learning the patterns of pixel variation rather than a static background image.
Thus the proposed approach achieves promising performance for the canoe video.

As for the case of the shadow scene, ``peopleInShade'' is a typical example with prevalent hard and soft shadows. 
For traditional approaches, these shadow regions are usually segmented as foreground since they also movie with the objects. 
Therefore, traditional methods like PAWCS, WeSamBE and SharedModel falsely segment part of shadows as moving objects. 
In addition, the foreground provided by IUTIS-5 is incomplete on part of the pedestrian's body due to the interference of shades, 
because of the severe dependency on texture features. 
On the other hand, DeepBS performs well for this video benefiting from the utilization of CNN. 
However, the shape of pedestrians are slightly deformed as a result of the patch-wise processing in CNN. 
In contrast, since our DPVL focusses on learning the pattern of pixels' variation in the shadow regions, 
the proposed approach successfully segments the shadow part as the background and achieves the highest performance in the category of shadow scene.

In the video ``corridor'' among the Thermal scene, there is no color information since the videos are obtained through a Thermal camera. 
Moreover, moving objects in these videos are exceedingly fuzzy and unclear, which is the main challenge for this category. 
WeSamBE, SharedModel and PAWCS successfully detect the target objects, because of a stable background in this indoor video. 
However, they fail to remove the reflections since their modeling ability has already reached a limit under the extreme condition of the thermal map. 
DeepBS, by contrast, succeeds in eliminating most of the reflections. 
Meanwhile, moving objects are also clearly divided from the background thanks to the strong modeling ability of CNN. 
However, due to the dependency of the edge feature, a small object was missed in the detection result. 
Fortunately, the proposed approach utilizes the pattern of pixels' variation, which is theoretically effective even in observations without color information. 
Consequently, our DPVTL performs much better than other algorithms, with most parts of the shadow being removed and the segmentation results become more accurate.

% \begin{table}[tab1]
\begin{table*}[!t]				% TABLE
\centering
\caption{Performance comparison of the proposed approach and some state-of-the-art algorithms on the video sequences from different categories in CDnet 2014. For each video, 100 frames were taken for training our FCN.}
\label{tab1}
\begin{tabular}{lllllllllllll}
\hline
Videos      & baseline & dyna.bg & cam.jitter & int.obj.m & shadow & thermal & bad.weat & low f.rate & night vid. & PTZ    & turbul. & overall \\ \hline
DeepBS\cite{Babaee2017deep}      & 0.9580   & 0.8761  & 0.8990     & 0.6097    & 0.9304 & 0.7583  & 0.8647   & 0.5900     & 0.6359     & 0.3306 & 0.8993  & 0.7458  \\
IUTIS-5\cite{Bianco2017TEC}     & 0.9567   & 0.8902  & 0.8332     & 0.7296    & 0.9084 & 0.8303  & 0.8289   & \textbf{0.7911}     & 0.5132     & 0.4703 & 0.8507  & 0.7717  \\
FTSG\cite{Wang2014FTSG}        & 0.9330   & 0.8792  & 0.7513     & 0.7891    & 0.8832 & 0.7768  & 0.8228   & 0.6259     & 0.5130     & 0.3241 & 0.7127  & 0.7283  \\
AAPSA\cite{RAMIREZALONSO2016990}       & 0.9183   & 0.6706  & 0.7207     & 0.5098    & 0.7953 & 0.7030  & 0.7742   & 0.4942     & 0.4161     & 0.3302 & 0.4643  & 0.6179  \\
CwisarDH\cite{Gregorio2014CwisarDH}    & 0.9145   & 0.8274  & 0.7886     & 0.5753    & 0.8581 & 0.7866  & 0.6837   & 0.6406     & 0.3735     & 0.3218 & 0.7227  & 0.6812  \\
PAWCS\cite{Charles2015PAWCS}       & 0.9397   & 0.8938  & 0.8137     & 0.7764    & 0.8934 & 0.8324  & 0.8059   & 0.6433     & 0.4171     & 0.4450 & 0.7667  & 0.7403  \\
SuBSENSE\cite{St-Charles2015SuBSENSE}    & 0.9503   & 0.8177  & 0.8152     & 0.6569    & 0.8986 & 0.8171  & 0.8594   & 0.6594     & 0.4918     & 0.3894 & 0.8423  & 0.7408  \\
SemanticBGS\cite{Braham2017Semantic} & 0.9604   & \textbf{0.9489}  & 0.8388     & 0.7878    & 0.9244 & 0.8219  & 0.8260   & 0.7888     & 0.5014     & 0.5673 & 0.6921  & 0.7892  \\
MBS\cite{Multimode_Background_Subtraction}         & 0.9287   & 0.7915  & 0.8367     & 0.7568    & 0.8262 & 0.8194  & 0.7980   & 0.6350     & 0.5158     & 0.5520 & 0.5858  & 0.7288  \\
WeSamBE\cite{2017_TCSVT_BG_7938679}     & 0.9413   & 0.7440  & 0.7976     & 0.7392    & 0.8999 & 0.7962  & 0.8608   & 0.6602     & 0.5929     & 0.3844 & 0.7737  & 0.7446  \\
ShareM\cite{2015_ICME_ShareModel}      & 0.9522   & 0.8222  & 0.8141     & 0.6727    & 0.8898 & 0.8319  & 0.8480   & 0.7286     & 0.5419     & 0.3860 & 0.7339  & 0.7474  \\
GMM\cite{Zivkovic2004}         & 0.8245   & 0.633   & 0.5969     & 0.5207    & 0.7370 & 0.6621  & 0.7380   & 0.5373     & 0.4097     & 0.1522 & 0.4663  & 0.5707  \\
RMoG\cite{Varadarajan2013}        & 0.7848   & 0.7352  & 0.7010     & 0.5431    & 0.7212 & 0.4788  & 0.6826   & 0.5312     & 0.4265     & 0.2470 & 0.4578  & 0.5735  \\ \hline
DPVT        & \textbf{0.9811}   & 0.9329  & \textbf{0.9014}     & \textbf{0.9595}    & \textbf{0.9467} & \textbf{0.9479}  & \textbf{0.8780}   & 0.7818     & \textbf{0.7737}     & \textbf{0.5957} & \textbf{0.9034}  & \textbf{0.8789} \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[!t]
\centering
\caption{Performance comparison of the proposed approach and some classical methods and deep-based method DBMF. For each video, 64 frames were taken for training our FCN.}
\label{tab2}
\begin{tabular}{llllllll}
\hline
Methods  & highway & office & Pedestrians & PETS2006 & Fall   & sofa   & overall \\ \hline
GMM\cite{Stauffer1999}      & 0.5788  & 0.2338 & 0.5202      & 0.6011   & 0.8026 & 0.5225 & 0.5432  \\
CodeBook\cite{WU2010739} & 0.8356  & 0.5939 & 0.7293      & 0.7808   & 0.3921 & 0.8149 & 0.6911  \\
ViBe\cite{Barnich2011_2011_TIP}     & 0.7535  & 0.6676 & 0.8367      & 0.6668   & 0.6829 & 0.4298 & 0.6729  \\
PBAS\cite{Hofmann2012Background}     & 0.8071  & 0.6839 & 0.7902      & 0.7280   & 0.3420 & 0.5768 & 0.6547  \\
P2M\cite{Yang2016P2M}      & 0.9160  & 0.3849 & 0.9121      & 0.7322   & 0.5819 & 0.4352 & 0.6604  \\
DBMF\cite{Yang2018DBMF}     & 0.9412  & 0.9236 & 0.8394      & 0.9059   & 0.8203 & 0.8645 & 0.8824  \\ \hline
DPVT     & \textbf{0.9888}  & \textbf{0.9819} & \textbf{0.9728}      & \textbf{0.9808}   & \textbf{0.9394} & \textbf{0.9333} & \textbf{0.9662}  \\ \hline
\end{tabular}
\end{table*}

    \begin{table*}[!t]
\centering
\caption{Performance comparison of the proposed approach and some state-of-the-art algorithms on video sequences from different categories in CAMO-UOW.}
\label{tab3}
\begin{tabular}{lllllllllll}
\hline
Methods  & MOG2\cite{ZIVKOVIC2006773} & FCI\cite{Baf2008FCI}  & LBA-SOM\cite{LBA-SOM2008} & PBAS & SuBSENSE & ML-BGS\cite{ML-BGS2007} & DECOLOR\cite{DECOLOR2013}       & COROLA\cite{SHAKERI201628} & FWFC\cite{Li2018CAMO}          & DPVT          \\ \hline
Video 1  & 0.79 & 0.88 & 0.8     & 0.9  & 0.89     & 0.89   & 0.92          & 0.8    & 0.94 & \textbf{0.96} \\
Video 2  & 0.82 & 0.79 & 0.8     & 0.82 & 0.88     & 0.8    & 0.83          & 0.58   & 0.96          & \textbf{0.98} \\
Video 3  & 0.88 & 0.86 & 0.85    & 0.91 & 0.9      & 0.8    & 0.9           & 0.82   & 0.94 & \textbf{0.95} \\
Video 4  & 0.89 & 0.9  & 0.76    & 0.93 & 0.78     & 0.88   & 0.95          & 0.87   & 0.94          & \textbf{0.98} \\
Video 5  & 0.84 & 0.86 & 0.82    & 0.83 & 0.82     & 0.8    & 0.82          & 0.75   & 0.91          & \textbf{0.98} \\
Video 6  & 0.93 & 0.87 & 0.77    & 0.95 & 0.92     & 0.95   & 0.97	      & 0.72   & 0.94          & \textbf{0.98}  \\
Video 7  & 0.76 & 0.83 & 0.88    & 0.91 & 0.87     & 0.79   & 0.91          & 0.83   & 0.96          & \textbf{0.99} \\
Video 8  & 0.83 & 0.87 & 0.85    & 0.87 & 0.93     & 0.86   & 0.86          & 0.68   & \textbf{0.96}          & \textbf{0.96} \\
Video 9  & 0.89 & 0.9  & 0.87    & 0.84 & 0.92     & 0.87   & 0.86          & 0.78   & 0.88          & \textbf{0.99} \\
Video 10 & 0.89 & 0.86 & 0.89    & 0.91 & 0.92     & 0.9    & 0.94          & 0.85   & 0.96          & \textbf{0.97} \\ \hline
average  & 0.85 & 0.86 & 0.83    & 0.89 & 0.88     & 0.85   & 0.90          & 0.77   & 0.94          & \textbf{0.97} \\ \hline
\end{tabular}
\end{table*}
